--- 
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# Supplementary Materials for: *“Penalized rank-one approximation to functional partial least-squares regression over complex domains”*

> Authors: Harold A. Hernández-Roig (<haroldantonio.hernandez@uc3m.es>);
> M. Carmen Aguilera-Morillo; Eleonora Arnone; Rosa E. Lillo; Laura M.
> Sangalli.

## Overview

You can download this R Project to reproduce our simulation studies and check the three-dimensional (3D) animations of the estimated coefficient functions relative to the real data application. The repository is organized into three sub-folders: 

* Folder **Animated Betas** contains 3D animations of the estimated coefficient
functions from *Section 5: “Application to brain connectivity data”*.

* Folders **1D_simulations** and **2D_simulations** contains the scripts required
to reproduce the simulations in *Section 4: “Simulation studies”*. 

## Simulation studies

The simulations depend on the R package `penR1FPLS`. It can be installed as follows:

```{r, include = TRUE, eval=FALSE}
devtools::install_github("hhroig/penR1FPLS", dependencies = TRUE)
```
    
### One-dimensional domain

Run:
```{r, include = TRUE, eval=FALSE}
source("1D_simulations/main_1D.R")
```
to reproduce the simulations for data defined over a one-dimensional (1D) domain. The script creates a new folder with results, including plots.


### Two-dimensional planar domain

Run:
```{r, include = TRUE, eval=FALSE}
source("2D_simulations/main_2D.R")
```
to reproduce the simulations for data defined over a two-dimensional (2D) planar domain. The script creates a new folder with results, including plots.

### Parallel computing

By default the simulations run in parallel using the `doParallel` package. For example, in the one-dimensional case, the core script is executed using:
```{r, include = TRUE, eval=FALSE}
library(doParallel)
nodes_CL = detectCores()   # Detect number of cores to use
cl = makeCluster(nodes_CL) # Specify number of threads here
registerDoParallel(cl)

source("1D_simulations/simulations_1D.R", local = TRUE)

stopCluster(cl)
```
The simulations can be executed in series by commenting the lines with `doParallel` commands and sourcing the script as it is:
```{r, include = TRUE, eval=FALSE}
# library(doParallel)
# nodes_CL = detectCores()   
# cl = makeCluster(nodes_CL) 
# registerDoParallel(cl)

source("1D_simulations/simulations_1D.R", local = TRUE)

# stopCluster(cl)
```
