--- 
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# Supplementary Materials for: *“Penalized rank-one approximation to functional partial least-squares regression over complex domains”*

> Authors: Harold A. Hernández-Roig (<haroldantonio.hernandez@uc3m.es>);
> M. Carmen Aguilera-Morillo; Eleonora Arnone; Rosa E. Lillo; Laura M.
> Sangalli.

## Overview

* Folder **Animated Betas** contains 3D animations of the estimated coefficient
functions from Section 5: “Application to brain connectivity data”.

* Folders **1D_simulations** and **2D_simulations** contains the scripts required
to reproduce the simulations in Section 4: “Simulation studies”. The simulations
depend on the R package `penR1FPLS`.

## Installing the R package `penR1FPLS`

To install `penR1FPLS` in R use:

```{r, include = TRUE, eval=FALSE}
devtools::install_github("hhroig/penR1FPLS", dependencies = TRUE)
```
    

## 1D simulations

## 2D simulations
